\documentclass[12pt]{article}
\usepackage[british]{babel}
\usepackage{amsmath, amssymb, amsfonts, amscd}
\usepackage{latexsym}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{etoolbox}

\topmargin -15mm
\textwidth 170mm
\textheight 224mm
\oddsidemargin -7mm
\evensidemargin -7mm
\sloppy

\synctex=1

\newtoggle{full}
\togglefalse{full}

% pdflatex -jobname=AGcv AGcv_short.tex
% will write the output to AGcv.pdf

\begin{document}

\centerline{\large \bf Curriculum Vitae}
\vskip5mm
\centerline{\Large \bfseries A\normalsize LEX \Large G\normalsize AVRYUSHKIN}
\vskip5mm
\centerline{3\textsuperscript{rd} December 2015}
\vskip5mm

\centerline{\bf Contacts}
\begin{tabbing}
Residency Status:     \  \= Department of Computer Science \= \kill
Address:        \> Computational Evolution Group \\
		\> Department of Computer Science \\
		\> The University of Auckland\\
		\> Private Bag 92019\\
		\> Auckland 1142, New Zealand\\
Office:		\> Science Centre 303.367\\
Phone:		\> +64 9 373 7599 ext.\ 85506\\
Homepage:	\> \href{http://alex.gavruskin.com}{http://alex.gavruskin.com}\\
Email:		\> \href{mailto:a.gavruskin@auckland.ac.nz}{a.gavruskin@auckland.ac.nz}\\
\iftoggle{full}{
Residency Status: \>New Zealand permanent resident\\
Date of Birth:	\>  18\textsuperscript{th} January 1983\\
}{}
\end{tabbing}

\centerline{\bf Education}
\begin{tabbing}
2009 \ \ \= Ph.\,D.\ in Mathematics \= in \ \= \kill
2009       \> Ph.\,D.\ in Mathematics \>  from Sobolev Institute of Mathematics, Novosibirsk\\
                \>             \>  Thesis advisor: Professor Sergei S.\ Goncharov\\
2006       \> M.\,S.\ in Mathematics \>  from Novosibirsk State University (with Honours)\\
2004       \> B.\,S.\ in Mathematics \>  from Novosibirsk State University (with Honours)\\
\iftoggle{full}{
2000       \> Gold Medal High School Diploma, Novokuznetsk%\\
}{}
\end{tabbing}

\centerline{\bf Professional Activity}
\begin{tabbing}
September \=2009\=--\=November \=2009 \ \= Visitor Research fe \ \= \kill
February \>2012\>--\> present \> \> Research Fellow \> The University of Auckland (NZ)\\
                \>        \>   \>             \>          \>                          \> Department of Computer Science\\
\iftoggle{full}{
February \>2015\>--\>present\>  \> Affiliate   \> Fred Hutchinson Cancer Research Centre (US)\\
                \>        \>   \>             \>          \>                          \> Computational Biology Programme \\
August \>2013\>--\>July\>2014 \> Lecturer \> Auckland University of Technology (NZ)\\
                \>        \>   \>             \>          \>                          \> School of Computer and Mathematical Sciences\\
November       \>2012\>--\>June \>2013    \> Research Visitor \> National University of Singapore\\
\> \>\>\>          \>                                  \>School of Computing\\
September \>2009\>--\>December \>2014 \> Senior Lecturer     \> Irkutsk State University (RF)\\
                \>        \>   \>             \>          \>                          \>Institute of Mathematics and Computer Science\\
September \>2009\>--\>November \>2009 \> Research Visitor   \> University of Notre Dame (US)\\
                \>        \>   \>             \>          \>                          \>Department of Mathematics \\
April           \> 2009\>--\>August     \>2009              \> Research Assistant     \> Sobolev Institute of Mathematics (RF)\\
September \>2006\>--\>July            \>2009          \> GTA                          \> Novosibirsk State University (RF)\\
}{
September \>2009\>--\>December \>2014 \> Senior Lecturer     \> Irkutsk State University (RF)\\
                \>        \>   \>             \>          \>                          \>Institute of Mathematics and Computer Science\\
}
\end{tabbing}

\centerline{\bf Awards}
\begin{tabbing}
2009 \ \ \= \kill
2011       \> Dr of Science Scholarship for three years\\
           \> (This Award is a Russian analogue of New Zealand's Rutherford Discovery Fellowship) \\
2009       \> Siberian Fund for Algebra and Logic Award (2005--2009)\\
2008       \> Award for excellence in teaching (at ACM-ICPC North-Eastern European Regional Contest)\\
2007       \> Siberian Mathematical Journal Award (from Sobolev Institute of Mathematics)\\
2006       \> Best Student Scientific Work Award (from Novosibirsk State University)\\
2005       \> Maltsev Award (from Novosibirsk State University)\\
\end{tabbing}

\iftoggle{full}{
\centerline{\bf Publications}
}{
\centerline{\bf Recent publications}
}
\begin{itemize}
\item A.\,Gavryushkin and A.\,Drummond.
	The space of ultrametric phylogenetic trees.
	{\em arXiv preprint} \href{http://arxiv.org/abs/1410.3544}{arXiv:1410.3544}.
	Submitted to {\em Journal of Theoretical Biology} in September 2015.
	Software is available at
	\href{https://github.com/gavruskin/tauGeodesic}{https://github.com/gavruskin/tauGeodesic}
\item T.\,Stadler, T.\,Vaughan, A.\,Gavryushkin, S.\,Guindon, D.\,K\"uhnert, G.E.\,Leventhal, and A.\,Drummond.
	How well can the exponential-growth coalescent approximate constant-rate birth-death population dynamics?
	{\em Proceedings of the Royal Society B: Biological Sciences,} 282, 1806, 2015.
\item P.\,Gavryushkin, Z.\,Popov, K.\,Litasov, and A.\,Gavryushkin.
	Unbiased crystal structure prediction of $\mathrm{NiSi}$ under high pressure.
	{\em Journal of Applied Crystallography,} 48, 3, 906--908, 2015.
\item A.\,Gavryushkin, B.\,Khoussainov, and F.\,Stephan.
	Reducibilities among equivalence relations induced by recursively enumerable structures.
	{\em Theoretical Computer Science,} DOI: 10.1016/j.tcs.2015.11.042, 2015.
\item A.\,Gavryushkin.
	Decidable models of small theories.
	{\em Lobachevskii Journal of Mathematics,} 36, 4, 446--449, 2015.
\item A.\,Gavryushkin, B.\,Khoussainov, M.\,Kokho, and J.\,Liu.
	Dynamic algorithms for monotonic interval scheduling problem.
	{\em Theoretical Computer Science,} Vol.\,562, 227--242, 2014.
\item A.\,Gavryushkin and A.\,Nies.
	Universality for left-computably enumerable  metric spaces.
	{\em Lobachevskii Journal of Mathematics,} 35, 4, 292--294, 2014.
\item A.\,Gavryushkin, B.\,Khoussainov, M.\,Kokho, and J.\,Liu.
	Dynamic interval scheduling for multiple machines.
	{\em ISAAC 2014, Springer LNCS,} Vol.\,8889, 235--246, 2014.
\item A.\,Gavryushkin, S.\,Jain, B.\,Khoussainov, and F.\,Stephan.
	Graphs realised by r.\,e.\ equivalence relations.
	{\em Annals of Pure and Applied Logic,} 165, 7, 1263--1290, 2014.
\item A.\,Gavryushkin, B.\,Khoussainov, M.\,Kokho, and J.\,Liu.
	Dynamising interval scheduling: the monotonic case.
	{\em Combinatorial Algorithms,} LNCS 8288, 178--189, 2013.
\item A.\,Gavryushkin and B.\,Khoussainov.
	On decidable and computable models of theories.
	{\em Springer LNCS} Vol.\,7921, 200--209, 2013.
\item A.\,Gavryushkin, S.\,Jain, B.\,Khoussainov, and F.\,Stephan.
	Graphs realised by r.\,e.\ equivalence relations.
	{\em The Nature of Computation---CiE,} 110--119, 2013.	
\item A.\,Gavryushkin.
	On constructive models of theories with linear Rudin-Keisler ordering.
	{\em Journal of Logic and Computation,} 22, 4, 793--805, 2012.
\iftoggle{full}{
\item A.\,Gavryushkin.
	Computable models of Ehrenfeucht theories.
	{\em CRM Documents}, Centre de Recerca Matem\`atica, Bellaterra (Barcelona), Vol.\,11, 67--77, 2012.
\item A.\,Gavryushkin.
	A new spectrum of computable models.
	{\em Bulletin of ISU.
	Series: mathematics,} 4, 4, 7--20, 2010.
\item A.\,Gavryushkin.
	Computable limit models.
	{\em Programs, Proofs, Processes---CiE,} 188--193, 2010.
\item A.\,Gavryushkin.
	Computable limit models for Ehrenfeucht theories.
	{\em Bulletin of ISU.
	Series: mathematics,} 3, 2, 56--61, 2009.
\item A.\,Gavryushkin.
	Computable models of theories with linear Rudin-Keisler ordering.
	{\em Bulletin of NSU.
	Series: mathematics, mechanics, informatics,} 9, 2, 30--37, 2009.
\item A.\,Gavryushkin.
	Spectra of computable models for Ehrenfeucht theories.
	{\em Algebra and Logic,} 46, 3, 149--157, 2007.
\item A.\,Gavryushkin.
	On complexity of Ehrenfeucht theories with computable model.
	{\em Logical Approaches to Computational Barriers---CiE,} 105--108, 2006.
\item A.\,Gavryushkin.
	Complexity of Ehrenfeucht models.
	{\em Algebra and Logic,} 45, 5, 289--295, 2006.
\end{itemize}
}{
\end{itemize}
\newpage
}

\iftoggle{full}{
\centerline{\bf Invited Talks}
}{
\centerline{\bf Recent invited talks}
}
\begin{tabbing}
September \ \=2004 \ \ \ \= Notre Dame and Novosibirsk Universities \ \ \ \= \kill
November    \>2015          \>  {\em Computational Biology Group  Seminar}                      \> Seminar talk \\
            \>              \>  at ETH---Z\"urich                                    \> \\
February    \>2015          \>  {\em Matsen Group Seminar}                                     \> Seminar talk \\
            \>              \>  at Fred Hutchinson Cancer Research Centre                                    \> \\
February    \>2015          \>  {\em Workshop on Networks of Life}                                     \> Workshop talk \\
            \>              \>  at the University of Canterbury                                      \> \\
June    \>2014          \>  {\em Algebra and Mathematical Logic:}  \> Special session talk \\
            \>              \>  {\em Theory and Applications} in Kazan                                    \> \\
November    \>2013          \>  {\em Randomness Workshop}                                             \> Workshop  talk\\
            \>              \>  at the University of Auckland                                     \> \\
November    \>2012          \>  National University of Singapore                                          \> Seminar talk\\
\iftoggle{full}{
March    \>2012          \>  Auckland University of Technology                                          \> Seminar talk\\
}{}
October    \>2011          \> {\em Maltsev Meeting} in Novosibirsk                                            \> Plenary talk\\
October     \>2011          \>{\em Logic Seminar} at Cornell University                                      \> Seminar talk\\
September \>2011         \> {\em Southern Wisconsin Logic Colloquium}                                  \> Seminar talk\\
\iftoggle{full}{
November   \>2009       \> Computational Logic Seminar                                              \> Seminar talk\\
                   \>                 \> at CUNY Graduate Centre\\
October    \>2009          \> Logic Seminar at Cornell University                                      \> Seminar talk\\
October    \>2009          \> Logic Seminar                                                                      \> Seminar talk\\
                 \>                  \> at the University of Notre Dame\\
November   \>2007       \> {\em Maltsev Meeting} in Novosibirsk                                             \> Plenary talk\\
September   \>2006      \> Algebra and Logic Seminar                                                    \> Seminar talk\\
        \>                          \> at Novosibirsk State University\\
June    \>2005               \> Notre Dame and Novosibirsk Universities                              \> Seminar talk\\
           \>                        \> Joint Seminar on Constructive Models\\
November   \>2004       \> Algebra and Logic Seminar                                                    \> Seminar talk\\
                   \>                \> at Novosibirsk State University\\
}
{}
\end{tabbing}

\iftoggle{full}{
\centerline{\bf Contributed Talks}
\begin{tabbing}
September \ \=2004 \ \ \ \= Notre Dame and Novosibirsk Universities \ \ \ \= \kill
October     \>2015                \> {\em Alan Wilson Centre Annual Meeting}                                      \> Long talk\\
                                        \>                \>  at Massey University  \> \\
February    \>2015                \> {\em The Interface of Mathematics and Biology}                                      \> Long talk\\
                                        \>                \> {\em NZ Phylogenomics Meeting} in Dunedin  \> \\
February    \>2014          \>  {\em Workshop on Networks of Life}                                     \> Participant \\
            \>              \>  at the University of Canterbury                                      \> \\
June    \>2013                \> {\em Mathematical and Computational}                                      \> Participant\\
                                        \>                \> {\em Evolutionary Biology} in Montpellier \> \\
July    \>2013                \> {\em Computability in Europe} in Milan                                       \> Two contributed talks\\
July    \>2011                 \> {\em Infinity Conference} in Barcelona                                              \> Contributed talk\\
July    \>2011                 \> {\em Logic Colloquium} in Barcelona                                              \> Contributed talk\\
July    \>2010                 \> {\em Logic Colloquium} in Paris                                                     \> Contributed talk\\
June    \>2010                \> {\em Computability in Europe} in Azores                                       \> Contributed talk\\
May    \>2010                 \> {\em Maltsev Meeting} in Novosibirsk                                             \> Contributed talk\\
August \>2009         \> {\em Logic Colloquium} in Sofia                                                      \> Contributed talk\\
June    \>2008              \> {\em Computability in Europe} in Athens                                         \> Contributed talk\\
July   \>2007                 \> {\em Logic Colloquium} in Wroclaw                                               \> Contributed talk\\
July    \>2006                \> {\em Computability in Europe} in Swansea                                      \> Contributed talk\\
\end{tabbing}
}{}

\centerline{\bf Grants}

\begin{tabbing}
2010--2012 \ \ \= \kill
2012--2013       \> Associate Investigator of an FRDF grant from the University of Auckland.\\
		\> Contract \#\,2795185 for \$200,000.\\
2011--2013       \> Principal Investigator and Coordinator of a Russian Government Grant.\\
		 \> Contract \#\,16.740.11.0567 for US\$50,000.\\
2010--2012       \> Principal Investigator and Coordinator of a Russian Government Grant.\\
		 \> Contract \#\,$\Pi1227$ for US\$65,000.\\
2006--2010       \> Participant of a Russian Fund for Fundamental Research Grant.\\
2003--2009      \> Participant of a Russian President Grant.\\
\end{tabbing}

\iftoggle{full}{
\centerline{\bf Travel Grants}
\begin{tabbing}
2010--2012 \ \ \= \kill
2012--2013        \> School of Computing, National University of Singapore\\
2011                  \> University of Chicago, University of Wisconsin--Madison, and Cornell University\\
2011                  \> Participation in the Logic Colloquium 2011\\
2010                  \> Participation in the Logic Colloquium 2010\\
2010                  \> Participation in the Computability in Europe 2010\\
2009                  \> University of Notre Dame, Cornell University, and NYC University\\
2009                  \> Participation in the Logic Colloquium 2009\\
2008                  \> Participation in the Computability in Europe 2008\\
2008                  \> Participation in the Summer School Marktoberdorf 2008\\
2007                  \> Participation in the Logic Colloquium 2007\\
2006                  \> Participation in the Computability in Europe 2006\\
\end{tabbing}
}{}

\centerline{\bf Students}

\begin{tabbing}
2015--2016 \ \ \ 	\= Edwardo Reynold \ \ \ 	\= Intern \ \ \	\= The University of Auckland (University of Greifswald)	\= \kill
2015--2016      \> Lena Collienne       \> Intern       \> The University of Auckland (University of Greifswald)\\
2015--2016      \> Edwardo Reynolds	\> Intern       \> The University of Auckland\\
\end{tabbing}

\iftoggle{full}{
\centerline{\bf Teaching}
}{
\centerline{\bf Recent teaching}
}

\begin{tabbing}
2010--2012 \ \ \ \= Novosibirsk State University \ \ \ \= \kill
2012--2014        \> The University of Auckland             \> Discrete Structures in Maths and CS (CompSci\,225)\\
2013--2014       \> Auckland U of Technology       \> Engineering Mathematics I and II (715001/716001)\\
2013--2013       \> Auckland U of Technology       \> Finite Mathematics (715205)\\
2012--2012       \> Auckland U of Technology        \> Theory of Computation (717300)\\
2012--2012       \> The University of Auckland              \> Software Engineering Theory (SoftEng\,211)\\
\iftoggle{full}{
2010--2011       \> Irkutsk State University              \> Computable Model Theory\\
2009--2010       \> Irkutsk State University              \> Model Theory\\
2009--2011       \> Irkutsk State University              \> Mathematical Logic\\
2010--2011       \> Irkutsk State University              \> Discrete Mathematics\\
2009--2010       \> Irkutsk State University              \> Theory of Computation\\
2006--2009       \> Novosibirsk State University       \> Theory of Algorithms\\
2007--2009       \> Novosibirsk State University       \> Theoretical Programming\\
2007--2009       \> Novosibirsk State University       \> Mathematical Logic\\
2007--2008       \> Novosibirsk State University       \> Number Theory\\
\end{tabbing}
}{
\end{tabbing}
\newpage
}

\centerline{\bf Service to Department and University}
\begin{tabbing}
2009 \ \ \ \= Domains VIII and Computability Over Continuous Data Types \ \ \ \= \kill
2013          \> Auckland--Novosibirsk Workshop on       \> Co-Chair of the \\
              \> Algebra, Logic, Geometry, and Combinatorics      \> Programme Committee \\
2009          \> Maltsev Meeting                          \> Organising Committee\\
2007          \> Mathematics in the Modern World          \> Organising Committee\\
2007          \> Domains VIII and Computability Over Continuous Data Types     \> Organising Committee\\
2005          \> Asian Logic Conference                   \> Organising Committee%\\
\end{tabbing}

\noindent I am a regular reviewer for {\em AMS Mathematical Reviews} and a referee for highly reputable journals and conferences such as\\
$\bullet$ {\em Genome Biology and Evolution}\\
$\bullet$ {\em Journal of Mathematical Biology}\\
$\bullet$ {\em LICS Symposium}
\vskip30pt
\iftoggle{full}{
\flushright{This CV: \url{https://gavruskin.github.io/AGcv.pdf}}
}{
\flushright{This CV: \url{https://gavruskin.github.io/AGcv_short.pdf}}
}
\end{document}

